---
title: "First Knit"
author: "Demian Romero"
date: "Date, 2019"
output: 
  html_document:
    number_sections: true
    toc: true
---

### `r as.character(Sys.Date())`

```{r include=FALSE,echo=FALSE}
require(tidyverse)
if(!require("imager")) {install.packages("imager");require("imager")}

```

```{r echo=FALSE,out.width='100%'}
xx<-getwd()
Drive_ltr <- strtrim(xx,2)
yy <- str_glue("{Drive_ltr}\\AAA_Owner_Info\\My_photo.jpg")
my_pict <- load.image(yy)
plot(my_pict,axes=FALSE,main="I'm Confused")
```

# A Little Survey

Here are just a few questions so I can get to know you and so you can get practice submitting an assignment in Canvas.  For each question, insert your answer underneath. Make sure each answer is at the minimum a complete sentence with correctly spelled words and correct puncuation. Half the points in this assignment depend on your picture and name being correct!!  Be sure to put your photo in the AAA_Owner_Info folder and call it My_photo.jpg after first renaming the current one to Koala.jpg . 

##Where are you now?  
What row are you in, front,middle or back?  Do you usually choose a similiar row in other classes? What is the computer number where you are sitting?  How on a scale of 1 to 10 (1=low, 10=high) How you feel about periodic seat re-assignment, say how and why. Teams, have you ever worked on one in a class setting?  




###my answer     
  
I am sitting in the second row near the middle front of the class. I am siting at computer number 16. I do not like seat reassignments at all, I would give it a 1. I find seat reassignments distracting. I have worked on a team in a class setting.   
     


##Others and You?   
What name do you prefer to be called by your classmates and instructor, if your buddys call you something but you want me to call you something else - what would that be? 

###my answer     
I prefer to be called Demian by both my classmates, my friends and my mentors.
   
 




##Aspirations?   
What do you want to achieve in life?  What college subject do you think would be of the greatest interest to you? What degree or certificate are you trying to achieve?

###my answer     
  
I want to explore all of my interests. Curently college subjects are the problem. I keep adding extra classes because I am interested in them. However once I add the extra classes I am only a few classes from another degree. I am currently majoring in Anthropology, Landscape Construction and Enviromental Hoticulture.
 




##Past adventures?  
Have you ever gone to foreign countries, if so which ones, if not Where might you go in the future?  Have you ever been in the military, if so which branch, if not which branch would you choose if you got drafted, and why?

###my answer     
  
   I have been to Mexico, Canada and the U.K. I hope to go to Italy next summer. I have never been in the military. If I got drafted I would be in shock as I do not think they have a geriatric branch. I am over 40. 
  




##Why are you taking Math 115?  
What grade do you need to attain in stats to not upset your future plans, What is your plan?
 

###my answer     
  
I am taking Math 115 because it is a core requirement for my Anthropology degree. In order to keep my 4.0 I will need an A. I hope to graduate from AVC with a 4.0.   
 





##Homework Help and Getting around?  
On a scale of 1 to 10, where 1 is a total dummy (doesn't know a mouse from a keyboard) and 10 is a complete geek (knows computer stuff in and out) How do you rate yourself?  Do you have a computer you can use at home? If so, what kind is it (windows, Apple, Linux)? Do you have internet access at home?  
How do you get to class? Are there issues that limit when you can be at the college?Where and when did you attend high school?  Do you currently have a job?

###my answer   
  
   
I would rate myself as a 7 on computer stuff. I have several Windows machines, desktops and laptops at home. I also have internet access. I drive to class. I do work full time in pest control. I attended High School a long, long time ago in galaxy far, far away.   




